% Reference manual page: ArrangementLandmarkTraits.tex
% Package: Arrangement_2

\ccRefPageBegin
\begin{ccRefConcept}{ArrangementLandmarkTraits_2}

\ccDefinition
% ===========
The concept \ccRefName{} refines the general traits concept by adding
operations needed for the landmarks point-location strategy, namely ---
approximating points and (optionally) connecting points with a simple
$x$-monotone curve.

A model of this concept must define the \ccc{Approximate_number_type}, which
is used to approximate the coordinates of \ccc{Point_2} instances. It is
recommended to define the approximated number type as the built-in
\ccc{double} type. 

The type \ccc{Construct_x_monotone_curve_2} is optional. The functor
is given two \ccc{Point_2} objects and constructs
an \ccc{X_monotone_curve_2} that connects them. The curve is then
used by the point-location to shorten the path of the walk.

\ccRefines
\ccc{ArrangementTraits_2}

\ccTypes
% ======
\ccNestedType{Has_construct_x_monotone_curve_2_category}
  {indicates whether the nested functor \ccc{Construct_x_monotone_curve_2} is
  provided. It must be convertible to \ccc{Tag_true} or \ccc{Tag_false}.} 

\ccNestedType{Approximate_number_type}%
  {The number type used to approximate point coordinates.}

\ccHeading{Functor Types}
% =======================
\ccThree{Construct_x_monotone_curve_2}{}{\hspace*{14cm}}
\ccThreeToTwo
\ccNestedType{Approximate_2}%
  {Models the concept \ccc{ArrTraits::Approximate_2}.}

\ccNestedType{Construct_x_monotone_curve_2}%
  {Required only if the \ccc{Has_construct_x_monotone_curve_2_category} category is convertible to
  \ccc{Tag_true}.
  Models the concept \ccc{ArrTraits::ConstructXMonotoneCurve_2}.}

\ccCreationVariable{traits}
% \ccCreation
% ===========

\ccHeading{Accessing Functor Objects}
% ===================================
\ccMethod{Approximate_2 approximate_2_object() const;} {}
\ccGlue
\ccMethod{Construct_x_monotone_curve_2 
          construct_x_monotone_curve_2_object() const;}
          {Required only if
          the \ccc{Has_construct_x_monotone_curve_2_category} category
          is convertible to~\ccc{Tag_true.}}

\ccHasModels
% ==========
\ccc{CGAL::Arr_non_caching_segment_basic_traits_2<Kernel>}\\
\ccc{CGAL::Arr_non_caching_segment_traits_2<Kernel>}\\
\ccc{CGAL::Arr_segment_traits_2<Kernel>}\\
\ccc{CGAL::Arr_linear_traits_2<Kernel>}\\
\ccc{CGAL::Arr_polyline_traits_2<SegmentTraits>}\\
\ccc{CGAL::Arr_conic_traits_2<RatKernel,AlgKernel,NtTraits>}\\
\ccc{CGAL::Arr_rational_function_traits_2<AlgKernel>}\\
\ccc{CGAL::Arr_circle_segment_traits_2<Kernel>}\\
\ccc{CGAL::Arr_Bezier_curve_traits_2<RatKernel,AlgKernel,NtTraits>}\\
\ccc{CGAL::Arr_curve_data_traits_2<Tr,XData,Mrg,CData,Cnv>}\\


\ccSeeAlso
%=========
\ccc{ArrangementTraits_2}\lcTex{(\ccRefPage{ArrangementTraits_2})}

\end{ccRefConcept}
\ccRefPageEnd

%%%%%%%% Functors %%%%%%%%
% ========================

%%%%%%%% Approximate_2
\ccRefPageBegin
\begin{ccRefConcept}{ArrTraits::Approximate_2}
\ccRefines{Functor}

\ccHasModels\ccc{ArrangementLandmarkTraits_2::Approximate_2}

\ccCreationVariable{fo}

\ccMethod{Approximate_number_type operator()( ArrTraits::Point_2 p,
                                              int i);}{%
  returns an approximation of \ccc{p}'s $x$-coordinate (if \ccc{i == 0}),
  or of \ccc{p}'s $y$-coordinate (if \ccc{i == 1}).}
\end{ccRefConcept}
\ccRefPageEnd

%%%%%%%% ConstructXMonotoneCurve_2
\ccRefPageBegin
\begin{ccRefConcept}{ArrTraits::ConstructXMonotoneCurve_2}
\ccRefines{Functor}

\ccHasModels\ccc{ArrangementLandmarkTraits_2::Construct_x_monotone_curve_2}

\ccCreationVariable{fo}

\ccMethod{ArrTraits::X_monotone_curve_2 operator() ( ArrTraits::Point_2 p1,
                                                     ArrTraits::Point_2 p2);}{%
  returns an $x$-monotone curve connecting \ccc{p1} and \ccc{p2} (i.e., the
  two input points are its endpoints).}
\end{ccRefConcept}
\ccRefPageEnd

